
\chapter{Expected Results and Evaluation Metrics}
\section{Methodology Implementation}
\subsection{Geometric camera Callibration}
Camera calibration has been completed for all three cameras, using [N] checkerboard image pairs per camera. Table~\ref{tab:reprojection_error} reports the resulting mean reprojection error per camera, all within acceptable bounds for accurate triangulation.
\begin{table}[ht]
\centering
\caption{Camera Reprojection Errors}
\label{tab:reprojection_error}
\begin{tabular}{lc}
\toprule
\textbf{Camera} & \textbf{Projection Error (px)} \\
\midrule
Camera 1 (Front) & X.XX \\
Camera 2 (Left)  & X.XX \\
Camera 3 (Right) & X.XX \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Parallel Multi-Modal Keypoint Extraction}
 MediaPipe Pose Landmarker and MediaPipe Hands have been integrated and tested across all three synchronized camera streams. Live landmark overlays confirming correct detection across all views are shown in Figure 4-6(same ss). The pipeline retains only the shoulder (landmarks 11, 12), elbow (13, 14), and wrist (15, 16) points from MediaPipe Pose's 33-point topology, alongside all 21 points from MediaPipe Hands per detected hand.
 % need to insert an screenshot of a real person's arm/hand, captured live by your webcam(s), with MediaPipe's landmark dots and skeleton connections drawn directly on top of the video frame — proving detection is actually running on your real setup, not a mockup. we also have demo video so maybe not needed.idkkk
\subsubsection{Confidence-Weighted Triangulation}
Confidence-weighted triangulation (Equation~\ref{eq:4-3}) has been implemented and validated across the full three-camera configuration. Reconstruction accuracy was assessed against a physically measured reference segment (e.g., [XX] cm forearm distance), yielding a mean absolute error of [X.XX] cm across [N] trials.

\subsection{Vector Proportional Retargeting}
Vector-proportional retargeting has been implemented, normalizing captured human joint vectors to the Kuka IIWA URDF model's link lengths as described in Equation~\ref{eq:4-4}, preventing joint hyper-extension during simulation.

\subsection{Articulated Kinematic Setup within PyBullet}
The PyBullet simulation environment has been implemented using the Kuka IIWA URDF manipulator model, rendering physically accurate joint movement in real time. Figure 4-7(same ss) shows the simulated arm replicating captured human motion.
% need to insert screenshot of the actual PyBullet simulation window, open and rendering, with the Kuka IIWA robotic arm posed in a way that visibly matches (or is clearly derived from) a captured human arm position — proving the IK mapping from human motion to robot joints is actually functioning.but again demo vid so idkkkk
\subsection{Damped Least Squares Inverse Kinematics}
The DLS-based IK solver(Equation~\ref{eq:4-5}) has been implemented and validated, successfully mapping reconstructed $3$D wrist positions to joint configurations without encountering singularity-related failures during testing. 

\subsection{Automated Data Factory Serialization}
Automated CSV dataset serialization has been implemented, producing per-frame records of 3D joint coordinates, computed joint angles, and timestamps as defined in Equation~\ref{eq:4-6}. Table~\ref{tab:sample_dataset} shows a representative sample of the generated dataset.

\begin{landscape}

\begin{table}[p]
\centering
\caption{Sample Rows from Generated Dataset}
\label{tab:sample_dataset}

\begin{tabular}{ccccccccccccc}
\toprule
\textbf{$t$ (s)} &
\textbf{shoulder\_x} &
\textbf{shoulder\_y} &
\textbf{shoulder\_z} &
\textbf{elbow\_x} &
\textbf{elbow\_y} &
\textbf{elbow\_z} &
\textbf{wrist\_x} &
\textbf{wrist\_y} &
\textbf{wrist\_z} &
\textbf{$\theta_1$} &
\textbf{$\theta_2$} &
\textbf{$\theta_3$} \\
\midrule

XX & XX & XX & XX & XX & XX & XX & XX & XX & XX & XX & XX & XX \\

XX & XX & XX & XX & XX & XX & XX & XX & XX & XX & XX & XX & XX \\

\bottomrule
\end{tabular}

\end{table}

\end{landscape}


\section{Expected Results}

The proposed MotionBridge system is expected to provide a low-cost and real-time framework for human arm motion capture, simulation replication, and robotic dataset generation using only standard RGB cameras and open-source software tools. By integrating MediaPipe-based landmark detection, multi-camera triangulation, and PyBullet simulation, the system is expected to generate accurate three-dimensional representations of human arm and hand motion without requiring specialized depth sensors or wearable devices.

The system is expected to successfully detect shoulder, elbow, wrist, and finger landmarks from multiple camera views and reconstruct their corresponding 3D world coordinates through confidence-weighted triangulation. The reconstructed arm motion is expected to be replicated in real time within a PyBullet simulation environment using inverse kinematics-based robotic arm control.

Simultaneously, the system is expected to generate a structured dataset containing timestamped 3D coordinates of arm and finger joints, along with corresponding robotic arm joint angles. This dataset is intended to support future applications in robotic imitation learning, teleoperation, rehabilitation engineering, and human--robot collaboration.

Furthermore, the multi-camera architecture is expected to improve robustness against partial occlusions by utilizing redundant viewpoints, thereby maintaining reliable landmark reconstruction even when one camera view is temporarily obstructed. The complete pipeline is expected to operate on standard CPU-based hardware while maintaining near real-time performance.

\section{Evaluation Metrics}

The performance of the proposed system will be evaluated using quantitative and qualitative metrics that assess landmark detection quality, three-dimensional reconstruction accuracy, real-time performance, simulation responsiveness, dataset quality, and robustness to occlusions.

\subsection{Landmark Detection Performance}

The effectiveness of MediaPipe Pose and MediaPipe Hands in detecting arm and hand landmarks will be evaluated using standard classification metrics based on correctly and incorrectly detected landmarks.

\paragraph{1. Precision}

Precision measures the proportion of detected landmarks that are correctly identified.

\begin{equation}
Precision = \frac{TP}{TP+FP}
\end{equation}

where:
\begin{itemize}
    \item TP = True Positives
    \item FP = False Positives
\end{itemize}

\paragraph{2. Recall}

Recall measures the proportion of actual landmarks that are successfully detected.

\begin{equation}
Recall = \frac{TP}{TP+FN}
\end{equation}

where:
\begin{itemize}
    \item FN = False Negatives
\end{itemize}

\paragraph{3. F1-Score}

The F1-score provides a balanced measure of precision and recall.

\begin{equation}
F1 = 2 \times \frac{Precision \times Recall}{Precision + Recall}
\end{equation}

Higher precision, recall, and F1-score values indicate better landmark detection performance.

\subsection{Three-Dimensional Reconstruction Accuracy}

The accuracy of the reconstructed 3D joint coordinates will be evaluated by comparing reconstructed positions with known reference measurements or predefined calibration poses.

The Mean Reconstruction Error will be calculated as:

\begin{equation}
E_{mean} = \frac{1}{N}\sum_{i=1}^{N}\left\|X_i-\hat{X}_i\right\|
\end{equation}

where:
\begin{itemize}
    \item $X_i$ represents the reference joint position,
    \item $\hat{X}_i$ represents the reconstructed joint position,
    \item $N$ represents the total number of evaluated joints.
\end{itemize}

Lower reconstruction error indicates better triangulation accuracy and more reliable 3D motion capture.

\subsection{Real-Time Processing Performance}

The computational efficiency of the proposed system will be evaluated using the following metrics:

\begin{itemize}
    \item Frames Per Second (FPS)
    \item Average processing time per frame
    \item CPU utilization
\end{itemize}

Frames Per Second (FPS) will be computed as:

\begin{equation}
FPS = \frac{\text{Total Processed Frames}}{\text{Total Execution Time}}
\end{equation}

The system is expected to maintain near real-time operation while processing multiple camera streams simultaneously.

\subsection{Simulation Replication Latency}

The responsiveness of the robotic arm simulation will be measured by calculating the delay between human motion capture and corresponding robotic arm movement within PyBullet.

Latency will be calculated as:

\begin{equation}
Latency = T_{simulation} - T_{capture}
\end{equation}

where:
\begin{itemize}
    \item $T_{capture}$ is the timestamp of landmark acquisition,
    \item $T_{simulation}$ is the timestamp of simulation update.
\end{itemize}

Lower latency values indicate better real-time motion replication performance.

\subsection{Dataset Completeness}

The quality and reliability of the generated dataset will be evaluated by measuring the percentage of frames containing valid joint information.

Dataset Completeness will be calculated as:

\begin{equation}
Completeness = \frac{\text{Valid Frames}}{\text{Total Frames}} \times 100
\end{equation}

A higher completeness percentage indicates successful landmark tracking and dataset generation throughout the recording session.

\subsection{Occlusion Robustness}

To evaluate the robustness of the proposed multi-camera framework, controlled occlusion experiments will be performed by partially blocking one or more camera views.

The following factors will be analyzed:

\begin{itemize}
    \item Landmark detection continuity
    \item Reconstruction accuracy under occlusion
    \item Percentage of successfully reconstructed joints
    \item Simulation stability during occluded conditions
\end{itemize}

The multi-camera configuration is expected to reduce tracking failures and improve reconstruction reliability compared to monocular camera systems.

\subsection{Overall System Evaluation}

The overall effectiveness of MotionBridge will be assessed by combining the above metrics to determine whether the system can provide accurate, real-time human arm motion capture and robotic dataset generation using only low-cost RGB cameras and standard computing hardware.

Successful completion of the project will be demonstrated through:

\begin{itemize}
    \item Reliable landmark detection,
    \item Accurate 3D joint reconstruction,
    \item Real-time robotic arm simulation,
    \item Low-latency operation,
    \item High dataset completeness,
    \item Robust performance under moderate occlusion conditions.
\end{itemize}

The results obtained from these evaluations will be used to assess the suitability of the proposed framework for future robotic imitation learning and human--robot interaction applications.